Final Project Draft #2

### 2022-04-26 draft2.Rmd
commit #3

```{r}
#Loading the packages
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(tidyverse)
library(lubridate) 
library(ggthemes)
library(plotly)
library(ggdark)
```

@@

```{r}
country_GDP <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
    col_types = cols(GDPM = col_number(), 
        GDP = col_number(), pop = col_number(), 
        GDPPC = col_number()))

healthy_data_2 <- healthy_data_dollars %>% 
  left_join(country_GDP,
            by = c("City" = "city"))

@@

#Happiness level by hours worked
```{r}
ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "",
       caption = "Data from: ADD LATER",
       x = "",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() 
```

>>>>

```{r}
#Loading the packages
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(tidyverse)
library(lubridate) 
library(ggthemes)
library(plotly)
library(ggdark)
library(maps)
library(ggmap)
```

@@

```{r}
supplemental_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQL_6se7aBLQSP92RgP5DkvQ_quTyzsTxskf9ZFpvE_5ifMS5whQ1Lr0JRNMtd1ZGAaVXlEEMECPMHr/pub?output=csv", 
    col_types = cols(GDPM = col_number(), 
        GDP = col_number(), pop = col_number(), 
        GDPPC = col_number()))

healthy_data_2 <- healthy_data_dollars %>% 
  left_join(supplemental_data,
            by = c("City" = "city"))

@@

```{r}
healthy_data_2 %>% 
  filter(country == "Canada")

# Get the map information
world <- get_stamenmap(
    bbox = c(left = -180, bottom = -57, right = 179, top = 82.1), 
    maptype = "terrain",
    zoom = 2)

# Plot the points on the map
ggmap(world) + # creates the map "background"
  geom_point(data = healthy_data_2 %>% 
  filter(country == "Canada"), 
             aes(x = Longitude, y = Latitude), 
             size = 0.5, color = "red") +
  theme_map()
```
